\begin{acknowledgements}
At the outset, we would like to express our gratitude to our professors Prof Gary Leung, Prof Zhu Fangming, Prof Liya Ding, Prof Xavier Xie, Prof Barry Shepherd, Prof Fan Zhenzhen, Prof Tian Jing, Prof Wang Aobo for imparting unto us the critical knowledge required for us to deliver effective results in this project. Their in-depth instruction and carefully curated teaching and workshops helped us in identifying areas to work on and techniques to utilise. We would like to acknowledge the entire staff at NUS ISS for making our onboarding to the course smooth and full of enthusiasm and engagement. We also wish to acknowledge the inviting and open collaborative culture in our course, which has made us feel at home and empowered to do our academic work with full focus.

We would like to especially acknowledge the personal and highly insightful guidance we received from Prof Gary Leung regarding the use cases we can identify to tackle in the field of quantitative research and financial engineering. He personally ensured at multiple occasions that our queries were answered and we were well prepared to work on our project. He encouraged us to pursue the project module in the field we were passionate about and consulted with us on our ideas and planned approach well before the proposal submission. We would like to thank his and Prof Liya Ding's feedback to us in our proposal call which set us in the right direction and kept us focused and aligned to the major task at hand.

We are thankful to Mr. Hunarpreet Singh of ArthAlpha, who agreed to act as a mentor and guide, who was always ready to provide professional recalibration related to the project. He and the company trusted our AI \& programming skills and gave us the opportunity to contribute to their critical projects. He was kind to meet with us on weekly basis to provide mentorship and solve our doubts, even during his busy time. He was always attentive and didn't let us feel at all like we were alone -- he took personal interest and wanted us to succeed. He extended motivation and honest feedback, and shared areas where we could improve. 

We would like to acknowledge our entire team wherein all teammates worked collaboratively divided the work smartly, and planned ahead to ensure timely cohesion and delivery, both on weekly basis to Hunar as well as over the course of the month. We are grateful for having such like minded and hard working team members.

We would like to acknowledge the LLM models ChatGPT 5, ChatGPT 5 Thinking, Perplexity Pro, Claude, Deepseek provided by the corporations OpenAI, Perplexity, Anthropic AI, DeepSeek AI which acted as our personal assistant and tutor. These tools helped us quickly draft first versions of any ideas that we wished to test, in data preparation, in understanding the approaches available to us, in recognising pros/cons/design decisions to consider, in figuring out the code, and finally in debugging any errors that we faced. Since these were like supercharged versions of the internet, a lot of our knowledge enquiries became much simpler and straightforward due to the presence of these tools and we were able to focus on the more important things core to our project, while saving time on tertiary activities like reading multiple Stack Overflow/Reddit pages for answers each time we faced a roadblock.

We would like to acknowledge that computational work involved in this
research work is partially/fully supported by NUS IT’s Research Computing
group under grant number NUSREC-HPC-00001. Thank you to National University of Singapore and to Institute of Systems Science for providing us with the necessary tools and environment required to hone our AI skills.
\end{acknowledgements}